The title

### 2020-09-02 manuscript/manuscript.Rmd
test hackmd
render plots

# Chunk options
knitr::opts_chunk$set(include = FALSE, echo = FALSE, fig.out = "100%", fig.width = 10)

@@

```{r exp1-behavior}
# Function for processing behavioral data
preproc_behav <- function(txt_fname){
  # Read log file
  dat <- suppressMessages(suppressWarnings(read_tsv(txt_fname)))
  # Rename some columns
  dat %<>% rename(participant = VPNummer, item = StimID) %>%
    # Add a column for the part of the experiment
    mutate(part = as_factor(Wdh - min(Wdh) + 1)) %>%
    # Remove filler stimuli (i.e. well-known objects)
    filter(bek_unbek != "bekannt")
  # Assign stimuli to conditions based on keywords and button presses
  known <- dat %>% filter(part == "1" & Tastencode %in% c(201, 251)) %>% pull(item)
  insight <- dat %>% filter(part == "2" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
  naive <- dat %>% filter(part == "2" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
  # Create a new condition column, excluding trials with knwon stimuli or without condition
  dat %<>% mutate(condition = as_factor(case_when(item %in% known ~ "Excl_known",
                                                  item %in% insight ~ "Insight",
                                                  item %in% naive ~ "Naive",
                                                  TRUE ~ "Excl_cond")))
  # In Experiment 3, we need an additional column for position (upright vs. inverted)
  if("richtig_inv" %in% dat$Bed){
    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
      # Return only relevant columns
      select(part, position, condition, participant, item, RT)
  } else {
    dat %<>% select(part, condition, participant, item, RT)}
  return(dat)}

@@

```{r exp1-table, include=TRUE, results="asis"}
# Check if models were computed already (delete the file to re-run)
if (file.exists("output/exp1-stats.RDS")){
  # Load models from file
  models_exp1 <- readRDS("output/exp1-stats.RDS")
} else {
  # Apply the modelling function and save to output folder
  models_exp1 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp1, control = ctrl_params,
                     specs = specs_exp12) %>% set_names(comps$name) %>% saveRDS("output/exp1-stats.RDS")}

# Define function to create ANOVA-style table
create_table <- function(models, stub.anova, stub.contrasts, caption, note){
  anov <- map(models, function(model){
    data.frame("stat" = paste0(format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2), " (", model$anova$NumDF,
                               ", ", format(round(model$anova$DenDF, 1), trim = FALSE, nsmall = 1), ")"),
               "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)) %>%
      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p))))}) %>%
    bind_cols() %>% set_rownames(c(stub.anova))
  cnames <- c("\\textit{Type III}", rep(c("\\textit{F} (\\textit{df})", "p" = "\\textit{p}"), 3))
  conts <- map(models, function(model){
    data.frame("stat" = paste0(format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2), " [",
                               format(round(model$contrasts$lower.CL, 2), trim = FALSE, nsmall = 2), ", ",
                               format(round(model$contrasts$upper.CL, 2), trim = FALSE, nsmall = 2), "]"),
               "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)) %>%
      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p)))) %>%
      add_row("stat" = "Est. [95% CI]", "p" = "\\textit{p}", .before = 1)}) %>% 
    bind_cols() %>% set_rownames(c("\\textit{Insight $-$  naive}", stub.contrasts))
  apa_table(list(anov, conts), col.names = cnames, escape = FALSE,
            col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N1}" = 4:5, "\\textbf{N400}" = 6:7),
            midrules = c(nrow(anov) + 1), font_size = "footnotesize", align = "lcccccc",
            caption = caption, note = note)}

# Apply the function to print the table
create_table(models_exp1, stub.anova = c("Part", "Insight", "Pt. × ins."),
             stub.contrasts = c("Part 1", "Part 2", "Part 3"),
             caption = "Results of linear mixed-effects regression models for Experiment 1",
             note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
```

```{r exp1-plotting, include=TRUE, fig.height=12}
# Import grand averaged evoked potentials from Python
evokeds_exp1 <- py$evokeds_dat_exp1

@@

```{r exp2-behavior}
# List of filenames for behavioral data
fnames_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE)

@@

```{r exp2-table, include=TRUE, results="asis"}
# Apply the function to print the table
create_table(models_exp2, stub.anova = c("Part", "Insight", "Pt. × ins."),
            stub.contrasts = c("Part 1", "Part 2", "Part 3"),
            caption = "Results of linear mixed-effects regression models for Experiment 2",
            note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")
```

```{r exp2-plotting, include=TRUE, fig.height=9}
# Import grand averaged evoked potentials from Python
evokeds_exp2 <- py$evokeds_dat_exp2

@@

```{r joint-table, include=TRUE, results="asis"}
# Apply the function to print the table
create_table(models_joint, stub.anova = c("Part", "Insight", "Experiment", "Pt. × ins.", "Pt. × exp.",
                                         "Ins. × exp.", "Pt. × ins. × exp."),
            stub.contrasts = c("Part 1", "Part 2", "Part 3"),
            caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
            note = "Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.")
```

```{r exp3-behavior}
# List of filenames for behavioral data
fnames_exp3 <- list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE)

@@

```{python exp3-preprocessing}
# List of raw EEG filenames
fnames_exp3 = sorted(glob.glob('data/exp3/EEG/*.vhdr'))

@@

```{r exp3-analysis}
# Re-import behavioral data
data_exp3 <- py$epochs_exp3$metadata

@@

```{r exp3-table, include=TRUE, results= asis"}
# Apply the function to print the table
create_table(models_exp3, stub.anova = c("Part", "Insight", "Position", "Pt. × ins.", "Pt. × pos.",
                                        "Ins. × pos.", "Pt. × ins. × pos."),
            stub.contrasts = c("Part 1, inverted", "Part 1, upright", "Part 2, inverted",
                               "Part 2, upright", "Part 3, inverted", "Part 3, upright"),
            caption = "Results of linear mixed-effects regression models for Experiment 3",
            note = "Pt. = part, ins. = insight, pos. = position, est. = estimate, CI = confidence interval.")
```

>>>>

# Chunk options
knitr::opts_chunk$set(include = FALSE, fig.align = "center", fig.out = "100%", fig.width = 10)

@@

```{r exp1-preparation}
# Function for processing behavioral data
preproc_behav <- function(txt_fname){
  # Read log file
  dat <- suppressMessages(suppressWarnings(read_tsv(txt_fname)))
  # Rename some columns
  dat %<>% rename(participant = VPNummer, item = StimID) %>%
    # Add a column for the part of the experiment
    mutate(part = as_factor(Wdh - min(Wdh) + 1)) %>%
    # Remove filler stimuli (i.e. well-known objects)
    filter(bek_unbek != "bekannt")
  # Assign stimuli to conditions based on keywords and button presses
  known <- dat %>% filter(part == "1" & Tastencode %in% c(201, 251)) %>% pull(item)
  insight <- dat %>% filter(part == "2" & grepl("richtig", Bed) & Tastencode %in% c(201, 202, 251, 252)) %>% pull(item)
  naive <- dat %>% filter(part == "2" & grepl("falsch", Bed) & Tastencode %in% c(203, 204, 253, 254)) %>% pull(item)
  # Create a new condition column, excluding trials with knwon stimuli or without condition
  dat %<>% mutate(condition = as_factor(case_when(item %in% known ~ "Excl_known",
                                                  item %in% insight ~ "Insight",
                                                  item %in% naive ~ "Naive",
                                                  TRUE ~ "Excl_cond")))
  # In Experiment 3, we need an additional column for position (upright vs. inverted)
  if("richtig_inv" %in% dat$Bed){
    dat %<>% mutate(position = as_factor(ifelse(grepl("inv", Bed), "Inverted", "Upright"))) %>%
      # Return only relevant columns
      select(part, position, condition, participant, item, RT)
  } else {
    dat %<>% select(part, condition, participant, item, RT)}
  return(dat)}

@@

```{r exp1-output, include=TRUE, results="asis", fig.height=12}
# Check if models were computed already (delete the file to re-run)
if (file.exists("output/exp1-stats.RDS")){
  # Load models from file
  models_exp1 <- readRDS("output/exp1-stats.RDS")
} else {
  # Apply the modelling function and save to output folder
  models_exp1 <- map(comps$name, compute_models, formula = form_exp12, data = data_exp1, control = ctrl_params,
                     specs = specs_exp12) %>% set_names(comps$name) %>% saveRDS("output/exp1-stats.RDS")}

# Define function to create ANOVA-style table
create_table <- function(models, stub.anova, stub.contrasts, caption, note){
  anov <- map(models, function(model){
    data.frame("stat" = paste0(format(round(model$anova$`F value`, 2), trim = FALSE, nsmall = 2), " (", model$anova$NumDF,
                               ", ", format(round(model$anova$DenDF, 1), trim = FALSE, nsmall = 1), ")"),
               "p" = format(round(model$anova$`Pr(>F)`, 3), trim = FALSE, nsmall = 3)) %>%
      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p))))}) %>%
    bind_cols() %>% set_rownames(c(stub.anova))
  cnames <- c("\\textit{Fixed effects}", rep(c("\\textit{F} (\\textit{df})", "p" = "\\textit{p}"), 3))
  conts <- map(models, function(model){
    data.frame("stat" = paste0(format(round(model$contrasts$estimate, 2), trim = FALSE, nsmall = 2), " [",
                               format(round(model$contrasts$lower.CL, 2), trim = FALSE, nsmall = 2), ", ",
                               format(round(model$contrasts$upper.CL, 2), trim = FALSE, nsmall = 2), "]"),
               "p" = format(round(model$contrasts$`p.value`, 3), trim = FALSE, nsmall = 3)) %>%
      mutate(p = ifelse(p == "0.000", "<.001", substr(p, 2, nchar(p)))) %>%
      add_row("stat" = "Est. [95% CI]", "p" = "\\textit{p}", .before = 1)}) %>% 
    bind_cols() %>% set_rownames(c("\\textit{Insight $-$  naive}", stub.contrasts))
  apa_table(list(anov, conts), col.names = cnames, escape = FALSE,
            col_spanners = list("\\textbf{P1}" = 2:3, "\\textbf{N1}" = 4:5, "\\textbf{N400}" = 6:7),
            midrules = c(nrow(anov) + 1), font_size = "footnotesize", align = "lcccccc",
            caption = caption, note = note)}

# Apply the function to print the table
create_table(models_exp1, stub.anova = c("Part", "Insight", "Pt. × ins."),
             stub.contrasts = c("Part 1", "Part 2", "Part 3"),
             caption = "Results of linear mixed-effects regression models for Experiment 1",
             note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")

# Import grand averaged evoked potentials from Python
evokeds_exp1 <- py$evokeds_dat_exp1

@@

```{r exp2-preparation}
# List of filenames for behavioral data
fnames_exp2 <- list.files("data/exp2/RT", pattern = ".txt", full.names = TRUE)

@@

```{r exp2-output, include=TRUE, results="asis", fig.height=9}
# Apply the function to print the table
create_table(models_exp2, stub.anova = c("Part", "Insight", "Pt. × ins."),
            stub.contrasts = c("Part 1", "Part 2", "Part 3"),
            caption = "Results of linear mixed-effects regression models for Experiment 2",
            note = "Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.")

# Import grand averaged evoked potentials from Python
evokeds_exp2 <- py$evokeds_dat_exp2

@@

```{r joint-output, include=TRUE, results="asis"}
# Apply the function to print the table
create_table(models_joint, stub.anova = c("Part", "Insight", "Experiment", "Pt. × ins.", "Pt. × exp.",
                                         "Ins. × exp.", "Pt. × ins. × exp."),
            stub.contrasts = c("Part 1", "Part 2", "Part 3"),
            caption = "Results of linear mixed-effects regression models for Experiments 1 and 2 combined",
            note = "Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.")
```

```{r exp3-preparation, eval=FALSE}
# List of filenames for behavioral data
fnames_exp3 <- list.files("data/exp3/RT", pattern = ".txt", full.names = TRUE)

@@

```{python exp3-preprocessing, eval=FALSE}
# List of raw EEG filenames
fnames_exp3 = sorted(glob.glob('data/exp3/EEG/*.vhdr'))

@@

```{r exp3-analysis, eval=FALSE}
# Re-import behavioral data
data_exp3 <- py$epochs_exp3$metadata

@@

```{r exp3-output, include=TRUE, results="asis", eval=FALSE}
# Apply the function to print the table
create_table(models_exp3, stub.anova = c("Part", "Insight", "Position", "Pt. × ins.", "Pt. × pos.",
                                        "Ins. × pos.", "Pt. × ins. × pos."),
            stub.contrasts = c("Part 1, inverted", "Part 1, upright", "Part 2, inverted",
                               "Part 2, upright", "Part 3, inverted", "Part 3, upright"),
            caption = "Results of linear mixed-effects regression models for Experiment 3",
            note = "Pt. = part, ins. = insight, pos. = position, est. = estimate, CI = confidence interval.")
```

### 2020-09-02 manuscript/manuscript.tex
add plots
render plots

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa7}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Title}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {}%
  {\par}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa7}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The title},
  pdfauthor={First Author1 \& Ernst-August Doelle1,2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Title}
\keywords{keywords\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {}%
  {\par}

@@

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp1-output}Results of linear mixed-effects regression models for Experiment 1}

\footnotesize{

\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
\textit{Type III} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
\midrule
Part & 10.30 (2,   23.4) & .001 & 13.56 (2,   23.9) & <.001 & 31.61 (2,   24.4) & <.001\\
Insight & 0.87 (1, 5299.9) & .352 & 0.96 (1, 5341.1) & .327 & 21.83 (1, 5210.4) & <.001\\
Pt. × ins. & 2.37 (2, 4616.5) & .094 & 5.34 (2, 4949.3) & .005 & 11.16 (2, 5058.3) & <.001\\
\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
Part 1 & 0.00 [-0.50, 0.49] & .991 & -0.17 [-0.62,  0.29] & .480 & -0.21 [-0.61, 0.18] & .292\\
Part 2 & -0.15 [-0.65, 0.35] & .553 & -0.66 [-1.12, -0.20] & .005 & 0.91 [ 0.51, 1.31] & <.001\\
Part 3 & 0.57 [ 0.08, 1.07] & .024 & 0.41 [-0.05,  0.87] & .080 & 0.99 [ 0.59, 1.39] & <.001\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\begin{figure}

{\centering \includegraphics{manuscript_files/figure-latex/exp1-output-1}

\caption{ }\label{fig:exp1-output}
\end{figure}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:exp2-output}Results of linear mixed-effects regression models for Experiment 2}

\footnotesize{

\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
\textit{Type III} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
\midrule
Part & 4.71 (2,   22.6) & .020 & 15.69 (2,   23.9) & <.001 & 67.52 (2,   24.1) & <.001\\
Insight & 0.05 (1, 5221.8) & .826 & 1.24 (1, 5215.3) & .266 & 18.64 (1, 5203.6) & <.001\\
Pt. × ins. & 1.72 (2, 3556.7) & .180 & 1.33 (2, 4746.9) & .266 & 8.01 (2, 4652.4) & <.001\\
\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
Part 1 & -0.17 [-0.72, 0.37] & .534 & -0.04 [-0.54, 0.45] & .858 & 0.02 [-0.44, 0.48] & .935\\
Part 2 & -0.32 [-0.87, 0.24] & .264 & -0.50 [-0.99, 0.00] & .050 & 1.31 [ 0.85, 1.77] & <.001\\
Part 3 & 0.38 [-0.18, 0.94] & .181 & 0.04 [-0.45, 0.54] & .864 & 0.45 [-0.01, 0.92] & .054\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Pt. = part, ins. = insight, est. = estimate, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\begin{figure}

{\centering \includegraphics{manuscript_files/figure-latex/exp2-output-1}

\caption{ }\label{fig:exp2-output}
\end{figure}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:joint-output}Results of linear mixed-effects regression models for Experiments 1 and 2 combined}

\footnotesize{

\begin{tabular}{lcccccc}
\toprule
 & \multicolumn{2}{c}{\textbf{P1}} & \multicolumn{2}{c}{\textbf{N1}} & \multicolumn{2}{c}{\textbf{N400}} \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \cmidrule(r){6-7}
\textit{Type III} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p} & \textit{F} (\textit{df}) & \textit{p}\\
\midrule
Part & 11.83 (2,    47.0) & <.001 & 28.64 (2,    47.8) & <.001 & 91.32 (2,    48.4) & <.001\\
Insight & 0.35 (1, 10554.2) & .554 & 1.64 (1,   124.2) & .203 & 38.73 (1, 10511.3) & <.001\\
Experiment & 0.34 (1,    46.2) & .564 & 2.29 (1,    46.1) & .137 & 4.56 (1,    46.4) & .038\\
Pt. × ins. & 3.96 (2,  9094.4) & .019 & 5.59 (2,  9889.2) & .004 & 15.71 (2, 10020.2) & <.001\\
Pt. × exp. & 0.03 (2,    47.0) & .971 & 0.53 (2,    47.8) & .595 & 2.47 (2,    48.4) & .095\\
Ins. × exp. & 0.62 (1, 10530.2) & .432 & 0.04 (1, 10325.9) & .838 & 0.03 (1, 10567.6) & .867\\
Pt. × ins. × exp. & 0.02 (2,  9094.8) & .976 & 0.63 (2,  9889.5) & .533 & 2.64 (2, 10020.5) & .072\\
\textit{Insight $-$  naive} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p} & Est. [95\% CI] & \textit{p}\\ \midrule
Part 1 & -0.07 [-0.44, 0.30] & .703 & -0.10 [-0.44,  0.24] & .563 & -0.10 [-0.41, 0.20] & .507\\
Part 2 & -0.22 [-0.59, 0.15] & .251 & -0.56 [-0.90, -0.21] & .002 & 1.09 [ 0.78, 1.39] & <.001\\
Part 3 & 0.49 [ 0.12, 0.86] & .010 & 0.25 [-0.10,  0.59] & .158 & 0.72 [ 0.41, 1.02] & <.001\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Pt. = part, ins. = insight, exp. = experiment, est. = estimate, CI = confidence interval.}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}
